PhD Thesis

### 2017-01-17 aosd13/paperBody.tex
Make title case consistent
Drop future work describing rest of thesis
Rearrange part I chapters

\section{Introduction}
In-memory collections of data often need efficient processing. For on-disk
data, efficient processing is already provided by database management systems~(DBMS) thanks to
their query optimizers, which support many optimizations specific to the domain
of collections. Moving in-memory data to DBMSs, however,
typically does not improve performance~\citep{Stonebraker07}, and query optimizers cannot
be reused separately since DBMS are typically monolithic and their optimizers deeply integrated.
A few collection-specific optimizations, such as shortcut
fusion~\citep{Gill93shortcut}, are supported by compilers for purely
functional languages such as Haskell. However, the implementation techniques for
those optimizations do not
generalize to many other ones, such as support for indexes. In
general, collection-specific optimizations are not supported by the general-purpose
optimizers used by typical (JIT) compilers.

@@

% XXX HACK
%\section{Automatic optimization with \textsc{\textbf{SQuOpt}}}
% Does not work well
\section{Automatic optimization with \\SQuOpt}

@@

\section{Implementation}
\label{sec:implementation}

@@

@@

\section{Related Work}
\label{sec:relwork}
This chapter builds on prior work on language-integrated queries, query optimization, techniques for DSL embedding, and other works on code querying.

@@

\section{Future Work}
As part of future work we plan to add support for \emph{incremental view
maintenance}~\citep{GlucheGrust97Incr} to \LoS. This would allow, for instance,
to update incrementally both indexes and query results.

@@

\section{Conclusions}

>>>>

\chapter{Introduction}
In-memory collections of data often need efficient processing. For on-disk
data, efficient processing is already provided by database management systems~(DBMS) thanks to
their query optimizers, which support many optimizations specific to the domain
of collections. Moving in-memory data to DBMSs, however,
typically does not improve performance~\citep{Stonebraker07}, and query optimizers cannot
be reused separately since DBMS are typically monolithic and their optimizers deeply integrated.
A few collection-specific optimizations, such as shortcut
fusion~\citep{Gill93shortcut}, are supported by compilers for purely
functional languages such as Haskell. However, the implementation techniques for
those optimizations do not
generalize to many other ones, such as support for indexes. In
general, collection-specific optimizations are not supported by the general-purpose
optimizers used by typical (JIT) compilers.

@@

% XXX HACK
%\section{Automatic optimization with \textsc{\textbf{SQuOpt}}}
% Does not work well
\chapter{Automatic optimization with SQuOpt}

@@

\chapter{Implementing SQuOpt}
\label{sec:implementation}

@@

\chapter{Collections as a case study}
\label{sec:caseStudy}
In this chapter we discuss collections as a \emph{critical} case
study~\citep{flyvbjerg06five} for deep DSL embedding.

As discussed in the previous chapter, to support optimizations we require a deep embedding of the collections DSL\@.

\input{aosd13/pepm13/caseStudyGoals}

\subsection{Implementation: Expressing the interface in Scala}
\label{sec:intfScala}
\input{aosd13/pepm13/caseStudyImpl}

@@

\chapter{Discussion}
\label{sec:discussion}
\input{aosd13/pepm13/caseStudyDiscussion}
\pg{TODO: mention discussion with Jacques Carette. Maybe mention that in the technical report only?}

\chapter{Related work}
\label{sec:relwork}
This chapter builds on prior work on language-integrated queries, query optimization, techniques for DSL embedding, and other works on code querying.

@@

\chapter{Conclusions}

\section{Future work}
% As part of future work we plan to add support for \emph{incremental view
% maintenance}~\citep{GlucheGrust97Incr} to \LoS. This would allow, for instance,
% to update incrementally both indexes and query results.

@@
